\huge Modeling Intervention Strategies for TB Control in the United States

### 2013-07-26 in_progress/presentations/poster/reuMHC2013.tex
added a caption to net costs, savings graph on poster

@@

      \begin{block}{An Agent Based Implementation}
        Implementing an Agent Based Framework
  \end{columns}
\end{frame}
\end{document}

>>>>

      \begin{block}{TB Reduction Strategies for the United States}
        From the Hill model, we 
            \includegraphics[scale=1]{incidencePlotRedEnLTBI.pdf}
          \caption{caption here!}
          \label{fig:redEnLTBI_costs}

@@

        \begin{figure}[h]
          \begin{center}
            \includegraphics[scale=1]{EnLTBIRedGroupCost.pdf}
          \end{center}
          \caption{A graph of the cumulative implementation costs, savings, and 
                       net US health care system costs of reducing rates of LTBI in
                       Foreign-born arrivals by 50\%, 75\%, and 100\%.  To determine the 
                       implementation cost for each intervention, the average cost
                       to identify and treat entering Foreign-born individuals with LTBI
                       was set to be \$600, \$800, and \$1000 for the 50\%, 75\%, 
                       and 100\% reduction strategies respectively.}
          \label{fig:redEnLTBI_costs}
        \end{figure}
      \end{block}
    \end{column}
    \begin{column}{.3\textwidth}
      \begin{block}{An Agent Based Implementation}
        Implementing an Agent Based Framework
      \end{block}
    \end{column}
  \end{columns}
\end{frame}
\end{document}
